Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-16 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
调整表格位置

\section{Experiments}

@@

We use SiamFC++ as our base tracker, and the backbone Siamese network adopts GoogLeNet.
We implement our our approach in Pytorch and train our perturbations using 3 GTX 1080Ti GPUs.
We adopt GOT-10k \cite{GOT-10k}, COCO \cite{COCO}, ILSVRC-VID \cite{VID} and LaSOT \cite{LaSOT} and our training set.
We train the perturbations for 32768 iterations with a minibatch of 96 images (32 images per GPU).
The learning rate of the template perturbation $\epsilon_1$ is set to 0.1, and the learning rate of the adversarial patch is $\epsilon_2 = 0.5$.
We generate training samples following the strategy in SiamFC++.
During the training and the testing phase, the size of the template image is set to $127\times 127\times 3$, and the size of the search image is set to $303\times 303\times 3$.
In Equ. \ref{eq:loss}, we set $\alpha=1, \beta=1, \gamma=1, \eta=0.005, \sigma=10^{-5}$.

@@

We need to set a specific trajectories $B^{fake}=\{b^{fake}_i\}_1^{T}$ for each video in the dataset to achieve targeted attack, which we call the \textbf{Fake Trajectory}. We call the bounding box ground truth $B^{gt}=\{b^{gt}_i\}_1^T$ the \textbf{Real Trajectory}.
Manually labelling $B^{fake}$ for each video will be time-consuming, so we generate $B^{fake}$ based on $B^{gt}$.
Specifically, the fake trajectory follows the real trajectory and the boundary between $b^{fake}_i$ and $b^{gt}_i$ is 16 pixels apart.
%The size of $b^{fake}_0$ is the same as $B^{gt}_0$ and the size of $b^{fake}_i$
The bounding box size of the fake trajectory gradually changes from the size of $S^{gt}_0$ to $64\times 64$.

\subsubsection{Image Quality Assessment}: We use structural similarity (SSIM) to evaluate the quality of the template perturbation $\delta$. The generated adversarial perturbation is difficult to be found when SSIM is close to 1 (see Table \ref{tab:iter}).

@@

We test our tracker on several benchmarks and results are gathered in Table \ref{tab:benchmark results}.
Note that, in the original SiamFC++ paper, they test different dataset using different trained model. But we test them using one single model. So on some datasets will drop slightly.

@@

As one of the most classical benchmarks for the object tracking task, the OTB benchmark provides a fair test for trackers. We conduct experiments on OTB2015 \cite{OTB} which contains 100 videos for tracker performance evaluation.
We use success precision and success scores to evaluate the performance of trackers on the OTB2015 dataset.
The precision encodes the proportion of frames for which the center of the tracking window is within 20 pixels of the ground-truth center. The success corresponds to the proportion of frames for which the overlap between the predicted and ground truth tracking window is greater than a given threshold.
After applying the universal perturbations to videos, the success score relative to $B^{gt}$ drops from 0.642 to 0.035, indicating that our method can fool the state-of-the-art SiamFC++ tracker effectively.
%The success score relative to $B^{gt}$ on the clean videos is 0.642. The success score relative to $B^{gt}$ on the adversarial videos is 0.035. The success score relative to $B^{fake}$ on the adversarial videos is 0.842.

@@

With a large number of video sequences, LaSOT (Largescale Single Object Tracking) benchmark makes it impossible for trackers to overfit the benchmark, which achieves the purpose of testing the real performance of object tracking.
Following onepass evaluation, we use three criteria including precision, normalized precision and success for evaluation.
The precision score relative to $B^{gt}$ on the clean videos is 0.514. The precision score relative to $B^{gt}$ on the adversarial videos is 0.013. The precision score relative to $B^{fake}$ on the adversarial videos is 0.820, indicating that our attack method is effective. Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations.

@@

We evaluate the transferability of our attacks on different backbones of SiamFC++: ShuffleNet \cite{ShuffleNet} and AlexNet \cite{AlexNet}.
The experimental results are shown in Table \ref{tab:backbone}. On SiamFC++-AlexNet, the AO relative to $B^{gt}$ drops from 0.72 to 0.196, which suggests that our perturbation can still work. However, our perturbations does not generalize well on SiamFC++-ShuffleNet, which we conjecture to be due to the significant difference of the network structure between googLeNet and ShuffleNet.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}

@@

We use SiamFC++ \cite{SiamFC++} as our base tracker, and the backbone Siamese network adopts GoogLeNet \cite{GoogLeNet}.
We implement our our approach in Pytorch and train our perturbations using 3 GTX 1080Ti GPUs.
We adopt GOT-10k \cite{GOT-10k}, COCO \cite{COCO}, ILSVRC-VID \cite{VID} and LaSOT \cite{LaSOT} and our training set.
We train the perturbations for 32768 iterations with a minibatch of 96 images (32 images per GPU).
The learning rate of the template perturbation $\epsilon_1$ is set to 0.1, and the learning rate of the adversarial patch is $\epsilon_2 = 0.5$.
We generate training samples following the strategy in SiamFC++.
During the training and the testing phase, the size of the template image is set to $127\times 127\times 3$, and the size of the search image is set to $303\times 303\times 3$.
In Equ. \ref{eq:loss}, we set $\alpha=1, \beta=1, \gamma=1, \eta=0.005, \sigma=10^{-5}$.

@@

We need to set a specific trajectories $B^{fake}=\{b^{fake}_i\}_1^{T}$ for each video in the dataset to achieve targeted attack, which we call the \textit{fake trajectory}. We call the bounding box ground truth $B^{gt}=\{b^{gt}_i\}_1^T$ the \textit{real trajectory}.
Manually labelling $B^{fake}$ for each video will be time-consuming, so we generate $B^{fake}$ based on $B^{gt}$.
Specifically, the fake trajectory follows the real trajectory and the boundary between $b^{fake}_i$ and $b^{gt}_i$ is 16 pixels apart.
%The size of $b^{fake}_0$ is the same as $B^{gt}_0$ and the size of $b^{fake}_i$
The bounding box size of the fake trajectory gradually changes from the size of $b^{gt}_1$ to $64\times 64$.

\subsubsection{Image Quality Assessment} We use structural similarity (SSIM) to evaluate the quality of the template perturbation $\delta$. The generated adversarial perturbation is difficult to be found when SSIM is close to 1 (see Table \ref{tab:iter}).

@@

We test the performance of our attack method on several benchmarks and results are gathered in Table \ref{tab:benchmark results}.
%Note that, in the original SiamFC++ paper, they test different dataset using different trained model. But we test them using one single model. So on some datasets will drop slightly.

@@

As one of the most classical benchmarks for the object tracking task, the OTB benchmark provides a fair test for trackers. We conduct experiments on OTB2015 \cite{OTB} which contains 100 videos for tracker performance evaluation.
We use success precision and success scores to evaluate the performance of trackers on the OTB2015 dataset.
The precision encodes the proportion of frames for which the center of the tracking window is within 20 pixels of the ground-truth center. The success corresponds to the proportion of frames for which the overlap between the predicted and ground truth tracking window is greater than a given threshold.
After applying the universal perturbations to videos, the success score relative to $B^{gt}$ drops from 0.642 to 0.035, indicating that our method can fool the state-of-the-art SiamFC++ tracker on OTB2015 effectively.
%The success score relative to $B^{gt}$ on the clean videos is 0.642. The success score relative to $B^{gt}$ on the adversarial videos is 0.035. The success score relative to $B^{fake}$ on the adversarial videos is 0.842.

@@

With a large number of video sequences, LaSOT (Largescale Single Object Tracking) benchmark \cite{LaSOT} makes it impossible for trackers to overfit the benchmark, which achieves the purpose of testing the real performance of object tracking.
Following onepass evaluation, we use three criteria including precision, normalized precision and success for evaluation.
The precision score relative to $B^{gt}$ on the clean videos is 0.514. The precision score relative to $B^{gt}$ on the adversarial videos is 0.013. The precision score relative to $B^{fake}$ on the adversarial videos is 0.820, indicating that our attack method is effective. Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations.

@@

We evaluate the transferability of our attacks on different backbones of SiamFC++: ShuffleNet \cite{ShuffleNet} and AlexNet \cite{AlexNet}.
The experimental results are shown in Table \ref{tab:backbone}. On SiamFC++-AlexNet, the AO relative to $B^{gt}$ drops from 0.72 to 0.196. However, our perturbations does not generalize well on SiamFC++-ShuffleNet, which we conjecture to be due to the significant difference of the network structure between googLeNet and ShuffleNet.
